Finding Quality Issues in SKOS Vocabularies

### 2012-03-23 analysis.tex
fixed table 1 columns

\begin{table}[h]
\label{tab:vocs}
\caption{Analyzed SKOS vocabularies}
\centering
\begin{tabular}{p{6cm}ccccccc}
\textbf{Vocabulary} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
\toprule
Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & 2010/08/25 & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
\hline
Geonames Ontology & 2.2.1 & 671 & 671 & 0 & 671 & 9 & 0 \\
\hline
Medical Subject Headings (MeSH) & ? & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
\hline
Peroxisome Knowledge Base (PXV) & 1.6 & 2112 & 3628 & 2695 & 1716 & 1 & 0 \\
\hline
Eurovoc & 5.0 & 6797 & 457788 & 18491 & 15512 & 128 & 0 \\
\hline
Integrated Public Sector Vocabulary (IPSV) & 2.00 & 4732 & 7945 & 13843 & 4483 & 3 & 0 \\
\hline
AGROVOC & 1.3 & 32035 & 620629 & 65934 & 32085 & 1 & 0 \\
\hline
DBpedia Categories & ? & 743410 & 740352 & 1490316 & 0 & 0 & 0 \\
\hline
University of Southampton Pressinfo & 2011/02/24 & 1125 & 0 & 0 & 0 & 0 & 0 \\
\hline
New York Times People (NYTP) & 2010/06/22 & 4979 & 4979 & 0 & 4979 & 1 & 0 \\
\hline
Library of Congress Subject Headings (LCSH) & ? & 459182 & 746076 & 595754 & 815816 & 19 & 0 \\
\hline
Meketre & 2011/07/07 & 422 & 569 & 1698 & 6 & 2 & 0 \\
\hline
Thesaurus for Economics (STW) & 8.06 & 6524 & 31189 & 57907 & 6531 & 1 & 0 \\
\hline
North American Industry Classification System (NAICS) & 2012 & 4175 & 0 & 8684 & 2235 & 1 & 0 \\
\hline
Thesaurus Landesverteidigungsakademie (LVAk) & n/a & 13411 & 17250 & 16346 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}
\label{vocabs}
\end{table}

>>>>

\begin{table}[h]
\label{tab:vocs}
\caption{Analyzed SKOS vocabularies}
\centering
\begin{tabular}{p{6cm}cccccccc}
\textbf{Vocabulary} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth. Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
\toprule
Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & 2010/08/25 & 171991 && 178776 & 50892 & 343980 & 9 & 0 \\
\hline
Geonames Ontology & 2.2.1 & 671 && 671 & 0 & 671 & 9 & 0 \\
\hline
Medical Subject Headings (MeSH) & ? & 24626 && 150617 & 38858 & 0 & 0 & 0 \\
\hline
Peroxisome Knowledge Base (PXV) & 1.6 & 2112 && 3628 & 2695 & 1716 & 1 & 0 \\
\hline
Eurovoc & 5.0 & 6797 && 457788 & 18491 & 15512 & 128 & 0 \\
\hline
Integrated Public Sector Vocabulary (IPSV) & 2.00 & 4732 && 7945 & 13843 & 4483 & 3 & 0 \\
\hline
AGROVOC & 1.3 & 32035 && 620629 & 65934 & 32085 & 1 & 0 \\
\hline
DBpedia Categories & ? & 743410 && 740352 & 1490316 & 0 & 0 & 0 \\
\hline
University of Southampton Pressinfo & 2011/02/24 & 1125 && 0 & 0 & 0 & 0 & 0 \\
\hline
New York Times People (NYTP) & 2010/06/22 & 4979 && 4979 & 0 & 4979 & 1 & 0 \\
\hline
Library of Congress Subject Headings (LCSH) & ? & 459182 && 746076 & 595754 & 815816 & 19 & 0 \\
\hline
Meketre & 2011/07/07 & 422 && 569 & 1698 & 6 & 2 & 0 \\
\hline
Thesaurus for Economics (STW) & 8.06 & 6524 && 31189 & 57907 & 6531 & 1 & 0 \\
\hline
North American Industry Classification System (NAICS) & 2012 & 4175 && 0 & 8684 & 2235 & 1 & 0 \\
\hline
Thesaurus Landesverteidigungsakademie (LVAk) & n/a & 13411 && 17250 & 16346 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}
\label{vocabs}
\end{table}
